Machine learning high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2023-03-13 qcd.tex
wording for perturbative treatment

    The renormalisation scale dependence of $\alpha_{s}$
    is governed by the Callan-Symanzik 
    $\beta$-function \cite{Callan:1970yg,Symanzik:1970rt}
    \begin{equation}\label{eqn:beta_fn}
        \mu_{R}^{2} \dfrac{\partial \alpha_{s}(\mu_{R}^{2})}{\partial \mu_{R}^{2}} = \beta(\alpha_{s}) \, ,
    \end{equation}
    where the $\beta$-function can be written as a perturbative
    expansion in $\alpha_{s}$
    \begin{equation}\label{eqn:beta_series}
        -\beta(\alpha_{s}) = \alpha_{s}\sum_{n=0}^{\infty}\left(\dfrac{\alpha_{s}}{4\pi}\right)^{n+1} \beta_{n}\, 
    \end{equation}
    where the coefficients $\beta_{n}$ have been computed
    up to $\beta_{4}$ \cite{Baikov:2016tgj,Luthe:2017ttg}.
    The solution to Eq. (\ref{eqn:beta_fn}) to first order
    is
    \begin{equation}\label{eqn:1l_alpha}
        \alpha_{s}(\mu_{R}^{2}) = \dfrac{1}{\frac{\beta_{0}}{4\pi}\log\left(\frac{\mu_{R}^{2}}{\Lambda_{\mathrm{QCD}}^{2}}\right)} \, ,
    \end{equation}
    where $\beta_{0} = (11C_{A} - 4T_{R}n_{f})/3$.
    In QCD, $C_{A}=3$ and $T_{R}=\frac{1}{2}$, meaning for
    $n_{f} < \frac{33}{2}$ the sign of $\beta_{0}$ is positive.
    In nature we have observed six flavours of quarks, so
    $\beta_{0} > 0$. In fact all $\beta$-coefficients
    computed to date are positive, meaning that $\alpha_{s}$
    decreases with increasing energy due to the minus sign
    in Eq. (\ref{eqn:beta_series}). This property is known as
    asymptotic freedom \cite{Gross:1973id,Politzer:1973fx},
    and is justification for treating QCD perturbatively
    when the energy scale is high, such as at collider experiments.
    The running of the coupling constant has been
    observed experimentally as illustrated in Figure~\ref{fig:alpha_s_running}.

>>>>

    The renormalisation scale dependence of $\alpha_{s}$
    is governed by the Callan-Symanzik 
    $\beta$-function \cite{Callan:1970yg,Symanzik:1970rt}
    \begin{equation}\label{eqn:beta_fn}
        \mu_{R}^{2} \dfrac{\partial \alpha_{s}(\mu_{R}^{2})}{\partial \mu_{R}^{2}} = \beta(\alpha_{s}) \, ,
    \end{equation}
    where the $\beta$-function can be written as a perturbative
    expansion in $\alpha_{s}$
    \begin{equation}\label{eqn:beta_series}
        -\beta(\alpha_{s}) = \alpha_{s}\sum_{n=0}^{\infty}\left(\dfrac{\alpha_{s}}{4\pi}\right)^{n+1} \beta_{n}\, 
    \end{equation}
    where the coefficients $\beta_{n}$ have been computed
    up to $\beta_{4}$ \cite{Baikov:2016tgj,Luthe:2017ttg}.
    The solution to Eq. (\ref{eqn:beta_fn}) to first order
    is
    \begin{equation}\label{eqn:1l_alpha}
        \alpha_{s}(\mu_{R}^{2}) = \dfrac{1}{\frac{\beta_{0}}{4\pi}\log\left(\frac{\mu_{R}^{2}}{\Lambda_{\mathrm{QCD}}^{2}}\right)} \, ,
    \end{equation}
    where $\beta_{0} = (11C_{A} - 4T_{R}n_{f})/3$.
    In QCD, $C_{A}=3$ and $T_{R}=\frac{1}{2}$, meaning for
    $n_{f} < \frac{33}{2}$ the sign of $\beta_{0}$ is positive.
    In nature we have observed six flavours of quarks, so
    $\beta_{0} > 0$. In fact all $\beta$-coefficients
    computed to date are positive, meaning that $\alpha_{s}$
    decreases with increasing energy due to the minus sign
    in Eq. (\ref{eqn:beta_series}). This property is known as
    asymptotic freedom \cite{Gross:1973id,Politzer:1973fx},
    and is the justification for treating QCD perturbatively
    when the energy scale is high, such as at collider experiments.
    The running of the coupling constant has been
    observed experimentally as illustrated in Figure~\ref{fig:alpha_s_running}.
